TRIK Studio: Technical Introduction

### 2017-02-09 2017-trikStudioEnglish/trikStudioEnglish.tex
added myself as an author

\author{
	\IEEEauthorblockN{Dmitry Mordvinov}
	\IEEEauthorblockA{
		Department of Software Engineering \\
		St.-Petersburg State University \\
		St.Petersburg, Russia \\
		Email: mordvinov.dmitry@gmail.com
	}
\and
	\IEEEauthorblockN{Yurii Litvinov}
	\IEEEauthorblockA{
		Department of Software Engineering \\
		St.-Petersburg State University \\
		St.Petersburg, Russia \\
		Email: y.litvinov@spbu.ru 
	}
}

>>>>

\author{
	\IEEEauthorblockN{Dmitry Mordvinov}
	\IEEEauthorblockA{
		Department of Software Engineering \\
		St.-Petersburg State University \\
		St.Petersburg, Russia \\
		Email: mordvinov.dmitry@gmail.com
	}
\and
	\IEEEauthorblockN{Yurii Litvinov}
	\IEEEauthorblockA{
		Department of Software Engineering \\
		St.-Petersburg State University \\
		St.Petersburg, Russia \\
		Email: y.litvinov@spbu.ru 
	}
\and
	\IEEEauthorblockN{Timofey Bryksin}
	\IEEEauthorblockA{
		Department of Software Engineering \\
		St.-Petersburg State University \\
		St.Petersburg, Russia \\
		Email: t.bryksin@spbu.ru 
	}
}
